\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
Selection Committee}

% opening here
\opening{}
\raggedright 
\setlength{\parindent}{15pt}

This letter is in support of MIDN 1/c Sharat Nemani’s application to the Critical Language Scholarship (CLS) program. For the last two years, I have been Mr.~Nemani’s advisor on research projects in the Department of Weapons, Robotics, and Control Engineering at the United States Naval Academy. Mr.~Nemani has my highest recommendation.
 
In his sophomore year, Mr.~Nemani worked with a team of upperclass on a project to fly swarms of fixed-wing and quadrotor drones in head to head aerial competition against teams from West Point and the Air Force Academy. To ensure team readiness, Mr.~Nemani worked hard to prepare aircraft for flight, including aircraft the 1/c (seniors) had given up on. In the unfamiliar environment of the actual competition, Mr.~Nemani was a sponge, soaking in experiences that will be important in his future naval career. He has continued on related projects, learning to fly drones and inquiring about flight biomechanics. His capstone project is to plan and execute drone-related field work in a foreign country in support of ecological research on endangered sea turtles.
 
I have not had opportunity to work with Mr.~Nemani on learning spoken human languages, but he has picked up multiple computer languages, and symbolic and abstract concepts related to engineering, quite well. Mr.~Nemani is of South Asian heritage and a son of immigrants, and he is highly motivated to learn Punjabi. I believe it would add another important dimension to his future naval career, especially considering the importance of South and Central Asian languages and South Asian regional knowledge in current military operations.

\closing{~} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}