\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
Dr.~R.~Camilli\\
Woods Hole Oceanographic Institution\\
266 Woods Hole Road MS\#07\\
Woods Hole, MA 02543-1040}

% opening here
\opening{Dear Dr.~Camilli:}

I am happy to recommend MIDN 2/C Gregory Burgess for a summer fellowship at Woods Hole Oceanographic Institution. I have known Mr.~Burgess for 1.5 years; he was an outstanding student in my ES200 (Introduction to Systems Engineering) section covering embedded microcontrollers, C and Matlab. I am also familiar with WHOI, and was a Joint Program student in AOPE. 

Mr.~Burgess stood out for driving his team's Pokemon video game project to develop graphics, use object-oriented techniques, Matlab classes, and GUIs. He is now getting started in Python and ROS. In ES200, I was also impressed by his creativity in developing a swivel turret firing ping pong balls, using minimal materials. 

Our department focuses on robotics, controls, and autonomy. Since taking my class, Mr.~Burgess has worked on a small autonomous vehicle with a color sensor, Hall-effect sensor, and ultrasound rangefinder. It navigated a course, avoided an obstacle, and detected ``mines'' under the course. Mr.~Burgess also implemented a ship's autopilot heading control as part of our honors linear systems class. 

Aside from classroom experience, Mr.~Burgess has been underway in USS ANNAPOLIS (SSN-760). He was part of the sonar division and stood watch under instruction as helmsman/planesman, basic sonar operator, and in fire control. This practical experience with undersea warfare could benefit navigation projects at WHOI or at-sea work on a research vessel. 

I understand the internship may involve gravity navigation on gliders. Here at USNA, we intend to have him work on vector magnetic navigation on a research project under CDR Paul Frontera. The techniques should be similar to bathymetric and gravity navigation work he would do at WHOI. 

Mr.~Burgess is an outstanding candidate and would fit in well at WHOI.
\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}