\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{% recipient address here
Stamps Scholarship Selection Committee}

% opening here
\opening{}

I am happy to recommend MIDN 3/C Lenny Davis for the Stamps Scholarship.  Mr.~Davis is an outstanding midshipman who embodies academic excellence, evidenced by his 4.0 QPR and \#1 OOM, and has high potential for graduate study.  

I have been Mr.~Davis’ instructor in ES281C Intro to Drone Technology, the quadrotor version of our ``School of Drones''; in addition, Mr.~Davis is active in the Squad With Autonomous Teammates Challenge (SWAT-C), an ONR-funded effort to examine how autonomy at a squad level can impact Marine Corps operations in a one-block war. A goal of School of Drones is to build drone experience early so that midshipmen can reach graduate-level work in autonomy and system design by the time they are upperclass. 

I believe Mr.~Davis has found his passion in drones and autonomy. He was the first midshipman to complete building his FT Gremlin from scratch and is currently one of the top two pilots in the class. I strongly believe introducing Mr.~Davis to drone operation early will allow him to innovate further and take drones and autonomy further in his remaining years at USNA; potentially positioning him to be a leader in a future (autonomous) fleet. 

Mr.~Davis intends to pursue graduate education and is well situated to do so based on credits and his plans to take robotics \& controls engineering electives starting next semester while still a 3/C. I believe his early drone experiences will also set him up for outstanding work in graduate school. I am excited to see where Mr.~Davis goes with drones and autonomy, and expect him to drive future transformation wherever he ends up in the fleet.

\closing{~} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}